Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-29 WRITEUP/ms.tex
missing bracket
minor comments

In \Fig{h2density}, we show the probability distribution of H$_2$
number density $n_{\rm H2}$ for \flower~ during its accreting phase,
including the contribution from the gas within 3.5 kpc from the
galaxy center. 
%
We note that the distribution is almost flat for $n_{\rm
  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
are found based on morphological analysis\footnote{For $n_{\rm
    H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$
  density field is significantly larger than zero. This implies that
  the field is made of isolated components. See Fig. 6 in
  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
%mm [I moved the next sentence into the main text from the footnote.]
We also tested variations in
  $n_{\rm cut}$ range and found no qualitative differences (see
  \Sec{ncut}).
%mm
\MM{I am confused how H$_2$ can survive at such low number
  densities.  Is there some sort of hidden clumping factor at work
  here? Or is this due to the neglect of local photodissociating
  radiation? Either way, the point should be mentioned in section 3, I
guess.}

@@

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
all the evolutionary stages considered in this work, for each  $n_{\rm
  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
  is the case for each ncut.} \MM{I am afraid I am also confused by
  this, for two reasons.  First, if I understand the Figure, the
  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E7
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs identified in the accreting phase \MM{In
  Figure  of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
\label{fig:MR}}
\end{figure*}

>>>>

In \Fig{h2density}, we show the probability distribution of H$_2$
number density $n_{\rm H2}$ for \flower~ during its accreting phase,
including the contribution from the gas within 3.5 kpc from the
galaxy center. 
%
We note that the distribution is almost flat for $n_{\rm
  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
are found based on morphological analysis\footnote{For $n_{\rm
    H2}\gtrsim1$\,\cc the fourth Minkowsky functional of the H$_{2}$
  density field is significantly larger than zero. This implies that
  the field is made of isolated components. See Fig. 6 in
  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
%mm [I moved the next sentence into the main text from the footnote.]
We also tested variations in
  $n_{\rm cut}$ range and found no qualitative differences (see
  \Sec{ncut}).
%mm
\MM{I am confused how H$_2$ can survive at such low number
  densities.  Is there some sort of hidden clumping factor at work
  here? Or is this due to the neglect of local photodissociating
  radiation? Either way, the point should be mentioned in section 3, I
guess.}
\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
 what one expects for purely H2 regions.}

@@

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
all the evolutionary stages considered in this work, for each  $n_{\rm
  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
  is the case for each ncut.} \MM{I am afraid I am also confused by
  this, for two reasons.  First, if I understand the Figure, the
  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E7
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} 
\DL{Since we don't resolve the molecular clouds, the clouds are not fully molecular. The $M_{\rm cl}$ here is more 
like total gas mass. AP will add disclaimer in Section 3. Will double check 
Mcl for all ncut and address AF's comment.}
  Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCCs identified in the accreting phase \MM{In
  Figure  of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
Extrapolating the masses and sizes of MCCs of \flower along the \citet{Kauffmann10b} 
relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCCs are capable of high-mass \SF.
\label{fig:MR}}
}
\end{figure*}
